\bf Service Chain Placement in SDNs \thanks{Research supported in part by Network Programming (Neptune) Consortium, Israel.}

### 2017-11-02 src/chain.tex
layer

\section{Fault Tolerance}
In this section we consider the problem of a service chain placement when there 
is also demand for fault tolerance.
Formally, given a physical network, a virtual specification and a parameter 
$\phi \in \mathbb{N}$, a $\phi$-robust placement is a collection of $\phi$ placements,
$f_1,\ldots,f_\phi$,
that correspond to $\phi$ internal vertex disjoint physical paths. 
We are looking for a $\phi$-robust placement that minimize the total cost:
$$
\sum_{i = 1}^\phi \sum_j c(\alpha_j,f_i(\alpha_j))
$$

>>>>

\section{Fault Tolerance}
In this section we consider the problem of a service chain placement when there 
is also demand for fault tolerance.
Formally, given a physical network, a virtual specification and a parameter 
$\phi \in \mathbb{N}$, a $\phi$-robust placement is a collection of $\phi$ placements,
$f_1,\ldots,f_\phi$,
that correspond to $\phi$ internal vertex disjoint physical paths. 
We are looking for a $\phi$-robust placement that minimize the total cost:
$$
\sum_{i = 1}^\phi \sum_j c(\alpha_j,f_i(\alpha_j))
$$
In this section we discuss how to efficiently find an optimal 
(assuming integral polynomial bounded costs) 2-robust placement.
The algorithm presented here, however, can be generalized to find an optimal $\phi$-robust
placement for any $\phi$

\subsection{Failure of the Greedy Algorithm}
Here we give a simple example why the greedy algorithm fails badly.
By greedy we mean applying the previous algorithm once to find an optimal placement, 
then removing all the vertices from the resulted path and applying the same algorithm again
to find the second placement.
Consider the physical graph as described in Figure~\ref{fig:greedy-bad} and a virtual path of
two virtual functions $\alpha$ and $\beta$.
Assume latencies, bandwidth, and processing constraints are all negligible 
and assume the following cost function 
$c(1, \alpha) = c(2, \alpha) = 1-\varepsilon, c(1, \beta) = c(2, \alpha) = 1$.
The greedy algorithm is unable to find a 2-robust placement in this case - after the 
first iteration there is no path from $s$ to $t$ - while, clearly there is a 2-robust
placement that costs $4 - 2 \epsilon$.   
\begin{figure}
\caption{
\label{fig:greedy-bad}
}
\begin{center}
\input{fig-alg-bad-example}
\end{center}
\end{figure}

\subsection{Fault Tolerance on Layered Graph}
We first assume that the input graph is a directed layered graph, i.e.
$G = (\bigcup_{i = 1}^l L_i, A)$ where 
$A \subseteq \bigcup_{i = 1}^{l - 1} L_i \times L_{i+1}$.
We assume that the number of vertices in each layer is at least two, or otherwise a 2-robust 
placement does not exist.
The algorithm uses dynamic programming.
We find the optimal 2-robust placement for every  
combination of two physical vertices from the same layer, 
and every combination of two virtual functions.
Formally, given the input $(G = (V, E), \calG = (\calV, \calE), p, b, s, t, c)$
We define $ft(v_1, v_2, \alpha_1, \alpha_2)$ to be the optimal 2-robust placement of 2 chains
that start at $\sigma$ and end at $\alpha_1, \alpha_2$ respectively into 
(internal vertex disjoint) physical paths that start at $s$ and end at $v_1,v_2$ respectively.
One can verified that the following recursive formula holds:
$$
ft(v_1, v_2, \alpha_1, \alpha_2) = 
\min_{
\begin{subarray}{c}
u_1,u_2,(\beta_1,\beta_2:
\\
u_1
\\
asdf
\end{subarray}
}
$$

\subsection{Layered Graph Transformation}
Given a directed acyclic graph $G = (V, A)$, 
and let $\pi:V \to [n]$ be an arbitrary topological sorting of $G$ 
we transform it into a layered graph $G'$ by replacing every edge $(u, v)$ with a directed path of 
length (number of arcs) $\pi(v) - \pi(u)$ from $u$ to $v$.
We set the processing capacity of each internal vertex on this path to be zero,
and the bandwidth of the arcs along the path to be $b(u,v)$.
It is easy to see that the resulting graph is indeed a layered graph and that every placement
on $G$ corresponds to a placement on $G'$ with the same cost.
Figure~\ref{fig:layer-transform} depicts this process.
\begin{figure}
\caption{
\label{fig:layer-transform}
}
\begin{center}
\input{layer-transform}
\end{center}
\end{figure}
